Designing a modular architecture for building web-based psychological experiments

### 2021-08-23 paper.tex
Finish conclusion

\chapter{Conclusion}
Web-based scientific experiments offer higher statistical power at a lower cost and effort with only marginal disadvantages compared to traditional experiment settings. Magpie's client-side leverages the advantages of modern JavaScript frameworks to offer a simple yet powerful framework for building such experiments. Its conceptual structure facilitates realizing basic as well as complex and even interactive experimental paradigms, while striking a balance between usability and expressiveness. Provided under an open source license, magpie facilitates open science, and eases the replication process. Fully relying on the power of a Turing-complete programming language for implementing experiments allows extending the basic framework with additions such as Optimal Experiment Design methods with ease.

TODO: +analysis +future directions +more flow

>>>>

\chapter{Conclusion}
Web-based scientific experiments offer higher statistical power at lower cost and effort with only marginal disadvantages compared to traditional experiment settings. Many software packages that attempt to provide functionality for implementing web-based experiments lack sufficient expressiveness and flexibility. Magpie's client-side module in contrast leverages the advantages of modern JavaScript frameworks to offer a simple yet powerful framework for building such experiments. Its conceptual structure facilitates realizing basic as well as complex experiments including interactive and dynamic experimental paradigms, while striking a balance between usability and expressiveness. Provided under an open source license, magpie facilitates open science, and eases the replication process. Fully relying on the power of a Turing-complete programming language for implementing experiments allows extending the basic framework with additions such as Optimal Experiment Design methods with ease. Future directions for work on magpie include improved reliability measures as well as additional built-in experimental paradigms and improved interoperability with standard software in the field of social science experiments.
